### 2021-06-14 [Economics].tex
kpi

% !TEX root = paper.tex
\section{Economics}
\label{sec:economics}

\input{[Economics][Einleitung]}    % binde die Datei '[Economics][Einleitung].tex' ein
\input{[Economics][Goals]}    % binde die Datei '[Economics][Goals].tex' ein
\input{[Economics][Quantifizierung]}    % binde die Datei '[Economics][Quantifizierung].tex' ein
\input{[Economics][Token-Economics]}    % binde die Datei '[Economics][Token-Economics].tex' ein
\input{[Economics][Fazit]}    % binde die Datei '[Economics][Fazit].tex' ein