### 2021-06-14 [Vision].tex

% !TEX root = paper.tex
\section{Vision}
\label{sec:vision}
\todo{TODO}