### 2021-10-26 [NFT-Pass].tex

% !TEX root = paper.tex
\section{NFT-Pass}
\label{sec:nft-pass}
\todo{TODO}