### 2022-01-31 [05][Economics]/[Economics].tex
REFACTORING

% !TEX root = paper.tex
\section{Economics} 
\label{sec:economics}

\input{C:/Users/Slava/White-Paper/[05][Economics]/[Economics][Einleitung]}    % binde die Datei '[Economics][Einleitung].tex' ein
\input{C:/Users/Slava/White-Paper/[05][Economics]/[Economics][Goals]}    % binde die Datei '[Economics][Goals].tex' ein
\input{C:/Users/Slava/White-Paper/[05][Economics]/[Economics][Quantifizierung]}    % binde die Datei '[Economics][Quantifizierung].tex' ein
\input{C:/Users/Slava/White-Paper/[05][Economics]/[Economics][Token-Economics]}    % binde die Datei '[Economics][Token-Economics].tex' ein
\input{C:/Users/Slava/White-Paper/[05][Economics]/[Economics][Fazit]}    % binde die Datei '[Economics][Fazit].tex' ein