### 2022-01-31 [06][NFT-Pass]/[NFT-Pass][Konzept][Intrinsischer Wert].tex

% !TEX root = C:/Users/Slava/White-Paper/[06][NFT-Pass]/[NFT-Pass][Konzept].tex

\vspace{0.2cm}

\todo{TODO: intrinsischer Wert mittels Berechtigungen als Governance-Token}

\vspace{0.3cm}