### 2022-02-01 [06][NFT-Pass]/[NFT-Pass][Konzept][Design].tex

% !TEX root = C:/Users/Slava/White-Paper/[06][NFT-Pass]/[NFT-Pass][Konzept].tex

\subsubsection{Design}

\vspace{0.2cm}

\todo{TODO: Design}

\vspace{0.3cm}