### 2022-02-01 [06][NFT-Pass]/[NFT-Pass][Konzept][Intrinsischer Wert].tex

% !TEX root = paper.tex
\vspace{0.2cm}

\todo{TODO: intrinsischer Wert mittels Berechtigungen als Governance-Token}

\vspace{0.3cm}