### 2022-03-22 [12][Anhang]/[Anhang].tex
Strukturierung des Kapitels 'Pool-Economics'

% !TEX root = paper.tex

\section{Anhang}
\label{sec:anhang}

\vspace{0.3cm}

\input{[12][Anhang]/[Anhang][Textueller Input]}    % binde die Datei '[Anhang][Textueller Input].tex' ein
\newpage

\input{[Anhang][Token-Economics][Bonding Curves]} % binde die Datei '[Anhang][Token-Economics][Bonding Curves].tex' ein