### 2022-03-24 [B][Pools]/[Pools].tex

% !TEX root = paper.tex

\section{Project 'Pools'}
\label{sec:pools}

\subsection{Einleitung}
\label{sec:pools-einleitung}
\vspace{0.3cm}
\input{[B][Pools]/[Pools][Einleitung]}    % binde die Datei '[Pools][Einleitung].tex' ein

\subsection{Formalisierungen}
\vspace{0.3cm}
\input{[B][Pools]/[Pools][Formalisierung]}    % binde die Datei '[Pools][Formalisierung].tex' ein

\subsection{Pool-Erzeugung}
\vspace{0.3cm}
\input{[B][Pools]/[Pools][Erzeugung]}    % binde die Datei '[Pools][Erzeugung].tex' ein

\subsection{Pool-Lifetime}
\vspace{0.3cm}
\input{[B][Pools]/[Pools][Lifetime]}    % binde die Datei '[Pools][Lifetime].tex' ein

\subsection{Pool-Liquidierung}
\vspace{0.3cm}
\input{[B][Pools]/[Pools][Liquidierung]}    % binde die Datei '[Pools][Liquidierung].tex' ein

\subsection{Pool-Vertrag}
\vspace{0.3cm}
\input{[B][Pools]/[Pools][Vertrag]}    % binde die Datei '[Pools][Vertrag].tex' ein

\subsection{Pool-Economics}
\vspace{0.3cm}
%\input{[B][Pools]/[Pools][Economic]}    % binde die Datei '[Pools][Economic].tex' ein
\input{[Pools][Economic]}