### 2022-03-24 [D][Anhang]/[Anhang].tex

% !TEX root = paper.tex

\section{Diverses}
\label{sec:anhang}

\vspace{0.3cm}

\input{[D][Anhang]/[Anhang][Textueller Input]}    % binde die Datei '[Anhang][Textueller Input].tex' ein
\newpage

\input{[D][Anhang]/[Anhang][Token-Economics][WUNDER-Token - Skizze eines möglichen Kreislaufs]} % binde die Datei '[Anhang][Token-Economics][WUNDER-Token - Skizze eines möglichen Kreislaufs].tex' ein
\newpage

\input{[D][Anhang]/[Anhang][Token-Economics][Bonding Curves]} % binde die Datei '[Anhang][Token-Economics][Bonding Curves].tex' ein